Cost-Benefit Analysis

### 2023-05-10 workflow/notebooks/cost-benefit-analysis.Rmd
Notes on Vince & Krishna's input

- use values from confusion matrix for one representative model on a test set.
  - number needed to screen
  - number needed to treat
  - number needed to benefit
- assumptions
  - cost of a non-severe case
  - cost of a severe case
    - days in icu, colectomy
  - cost of possible treatments:
    - abx: metronizadole, vancomycin, fidaxomycin
    - fmt, monoclonal antibodies

@@

## lit review

>>>>

- use values from confusion matrix for one representative model on a test set.
  - Number needed to screen (NNS) - the number of alerted patients the models must flag to identify 1 true positive. 
  - Number needed to treat (NNT) - the number of true positive patients one must treat for 1 patient to benefit from the treatment.
  - Number needed to benefit (NNB = NNS x NNT) - how many patients must be screened for 1 patient to benefit.
- assumptions
  - cost of a non-severe case
  - cost of a severe case
    - days in icu, colectomy
  - cost of possible treatments:
    - abx: metronizadole, vancomycin, fidaxomycin
    - fmt, bezlotoxumab (monoclonal antibodies)

@@

## treatment options & costs

- Vince: consider bezlotoxumab since it targets the toxin, mouse models show it reduces organ damage.
- Krishna: bezlotoxumab clinical trials didn't find signal for limiting severity.
